Fast gravitational wave parameter estimation without compromises

### 2023-07-21 src/tex/ms.tex
Update ms.tex
Add line number for ApJ submission
Comment 1 update
Address comment 2

% Old codes have trouble handling next gen data
% The PE results in the most recent catalog of GW events are produced by several
% community-developed PE codes
% \mi{what catalog do you mean? The LVK doesn't use PyCBC Inference}
There exist a number of prominent, community-developed PE codes, including
\textsc{LALInference} \citep{Veitch:2014wba}, \textsc{PyCBC Inference}
\citep{Biwer:2018osg}, and \textsc{Bilby}
\citep{Ashton:2018jfp,Romero-Shaw:2020owr}.  These packages have been tested by a
number of groups and are well regarded as standard tools. However, while these
tools have passed many robustness tests, they are known to be computationally
intensive. The exact amount of time needed to analyze one event depends on
factors like the duration and frequency of the signal, as well as features of
the specific waveform model. Typical runtimes for production-level analyses can
range from hours to weeks. This expense precludes iterating quickly on results,
launching large scale measurement simulations, or obtaining results in low
latency to inform astronomers for potential followup in real time.

@@

% More sample helps training normalizing flow
Yet, in our work, the use of accelerators provides two independent advantages
that tremendously benefit the parameter estimation process. First, using
accelerators allows us to run many independent MCMC chains simultaneously,
which benefits the training of the normalizing flow. Since we generate the data
we use to train the normalizing flow on the fly, the more independent data we
can feed to the training process, the higher chance the normalizing flow can
learn a reasonable representation of the global landscape of the target
distribution.  If we only used a small number of chains, we would be limited to
the correlated samples from each chain and we would have to run more sequential
steps to obtain the same amount of independent samples in the end---with more
chains the problem becomes parallelizable and we can obtain the same number of
training samples sooner. In other words, being able to use many independent
chains helps the normalizing flow learn the global landscape faster in wall
time.

>>>>

% Old codes have trouble handling next gen data
% The PE results in the most recent catalog of GW events are produced by several
% community-developed PE codes
% \mi{what catalog do you mean? The LVK doesn't use PyCBC Inference}
There exist a number of prominent, community-developed PE codes, including
\textsc{LALInference} \citep{Veitch:2014wba}, \textsc{PyCBC Inference}
\citep{Biwer:2018osg}, and \textsc{Bilby}
\citep{Ashton:2018jfp,Romero-Shaw:2020owr}.  These packages have been tested by a
number of groups and are well regarded as standard tools. However, while these
tools have passed many robustness tests, they are known to be computationally
intensive. The exact amount of time needed to analyze one event depends on
factors like the duration and frequency of the signal, as well as features of
the specific waveform model. Typical runtimes for production-level analyses can
range from hours to weeks.

@@

% More sample helps training normalizing flow
Yet, in our work, the use of accelerators provides two independent advantages
that tremendously benefit the parameter estimation process. First, using
accelerators allows us to run many independent MCMC chains simultaneously, which
benefits the training of the normalizing flow. Since we generate the data we use
to train the normalizing flow on the fly, the more independent data we can feed
to the training process, the higher chance the normalizing flow can learn a
reasonable representation of the target distribution.  If we only used a small
number of chains, we would be limited to the correlated samples from each chain
and we would have to run more sequential steps to obtain the same amount of
independent samples in the end---with more chains the problem becomes
parallelizable and we can obtain the same number of training samples sooner. In
other words, being able to use many independent chains helps the normalizing
flow approximating the target density faster in wall time.
